\documentclass[11pt]{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{tikz}

\title{
    Intelligent System 2\\
    Tutorial week 11: Abstract Argumentation\\
    \textbf{Solutions}
}

\author{
    Matteo Magnini\\
    \href{mailto:matteo.magnini@uni.lu}{matteo.magnini@uni.lu}
}

\date{
    6 May, 2026
}

\begin{document}

\maketitle

\section{Solutions}

\subsection{Exercise 1}

\textbf{Recall:} A set is conflict-free iff no arguments in it attack each other.

Attacks:
\[
a \leftrightarrow b,\quad b \to c,\quad c \leftrightarrow d
\]

\textbf{Conflict-free sets:}
\[
\emptyset,\ \{a\},\ \{b\},\ \{c\},\ \{d\},\ \{a,c\},\ \{a,d\},\ \{b,d\}
\]

\textbf{Maximal (naive candidates):}
\[
\{a,c\},\ \{a,d\},\ \{b,d\}
\]

These are maximal because adding any other argument introduces a conflict.

\subsection{Exercise 2}

\textbf{Naive extensions = maximal conflict-free sets:}
\[
\{a,c\},\ \{a,d\},\ \{b,d\}
\]

\textbf{Example non-naive:}
\[
\{a\}
\]
It is conflict-free but not maximal (can be extended to $\{a,c\}$).

\subsection{Exercise 3}

\textbf{Recall:} $E$ defends $a$ if for every attacker $b \to a$, there exists $c \in E$ such that $c \to b$.

Attacks:
\[
b \to a,\quad c \to b,\quad d \to c
\]

\begin{itemize}
    \item $\{a\}$:
    $a$ is attacked by $b$, but $\{a\}$ does not attack $b$ $\Rightarrow$ not defended.

    \item $\{c\}$:
    $c$ is attacked by $d$, but $\{c\}$ does not attack $d$ $\Rightarrow$ not defended.
\end{itemize}

\textbf{Admissible sets:}

\[
\emptyset,\ \{d\},\ \{b, d\}
\]

Explanation:
\begin{itemize}
    \item $\emptyset$: trivially admissible
    \item $\{d\}$: conflict-free and has no attackers
    \item $\{b, d\}$: conflict-free, $b$ is attacked by $c$, but $d$ attacks $c$, hence $b$ is defended by $\{b,d\}$; $d$ has no attackers
\end{itemize}

\subsection{Exercise 4}

\textbf{Recall:} Complete = admissible + contains all defended arguments.

Admissible sets:
\[
\emptyset,\ \{d\},\ \{b, d\}
\]

\textbf{Check completeness:}

\begin{itemize}
    \item $\emptyset$:
    does not defend any argument $\Rightarrow$ complete

    \item $\{d\}$:
    $d$ has no attackers, so it is trivially defended.

    However, $\{d\}$ also defends $b$:
    \[
    c \to b \quad \text{and} \quad d \to c
    \]
    hence $d$ attacks all attackers of $b$.

    Therefore, $\{d\}$ defends $b$ but $b \notin \{d\}$.

    $\Rightarrow$ $\{d\}$ does \textbf{not} contain all the arguments it defends.

    $\Rightarrow$ $\{d\}$ is \textbf{not} complete.
\end{itemize}

\textbf{Conclusion:}

\[
    \emptyset,\ \{b, d\}
\]
are the complete extensions.

\subsection{Exercise 5}

Attacks:
\[
b \to a,\quad c \to b,\quad d \to c
\]

\textbf{Grounded procedure (as in the slides):}

\begin{itemize}
    \item Step 0: all arguments are marked \textbf{undecided}

    \item Step 1: mark as \textbf{accepted (green)} any argument not attacked by a green or undecided argument

    The only such argument is:
    \[
    d
    \]

    \item Step 2: mark as \textbf{rejected (red)} any argument attacked by a green argument

    Since $d \to c$, we mark:
    \[
    c \text{ as rejected}
    \]

    \item Step 3: repeat Step 1

    Now, $b$ is attacked only by $c$, which is rejected, hence it is not attacked by any green or undecided argument.

    Therefore:
    \[
    b \text{ is accepted}
    \]

    \item Step 4: apply Step 2 again

    Since $b \to a$, we mark:
    \[
    a \text{ as rejected}
    \]
\end{itemize}

\textbf{Final labelling:}
\[
\text{accepted: } \{d, b\}, \quad
\text{rejected: } \{c, a\}
\]

\textbf{Grounded extension:}
\[
\{d, b\}
\]

\textbf{Conclusion:} the grounded extension is not empty.

\subsection{Exercise 6}

Attacks:
\[
a \leftrightarrow b,\quad c \to b
\]

\textbf{Complete extensions:}
\[
\emptyset,\ \{a\},\ \{a,c\}
\]

\textbf{Preferred (maximal complete):}
\[
\{a,c\}
\]

\textbf{Grounded:}
\[
\emptyset
\]

\textbf{Observation:}
Preferred $\neq$ grounded.

\subsection{Exercise 7}

Cycle:
\[
a \to b \to c \to a
\]

\textbf{Stable condition:}
Must attack all arguments outside the set.

Try candidates:
\begin{itemize}
    \item $\{a\}$: does not attack $c$
    \item $\{b\}$: does not attack $a$
    \item $\{c\}$: does not attack $b$
\end{itemize}

\textbf{Conclusion:}
No stable extension exists.

\subsection{Exercise 8}

Attacks:
\[
a \to b,\quad b \leftrightarrow c,\quad d \to a,\quad e \to c
\]

\textbf{Step 1: Conflict-free sets}

Recall: a set is conflict-free iff no two arguments in the set attack each other.

The conflict-free sets are:
\[
\emptyset,
\{a\},
\{b\},
\{c\},
\{d\},
\{e\},
\{a,c\},
\{a,e\},
\{b,d\},
\{b,e\},
\{c,d\},
\{d,e\},
\{b,d,e\}
\]

\textbf{Naive extensions}

Naive extensions are the $\subseteq$-maximal conflict-free sets.

We check which conflict-free sets cannot be extended further:

\[
\{a,c\},\quad
\{a,e\},\quad
\{c,d\},\quad
\{b,d,e\}
\]

Hence:
\[
\textit{naive}(AF)=
\{
\{a,c\},
\{a,e\},
\{c,d\},
\{b,d,e\}
\}
\]

\textbf{Step 2: Admissible sets}

Recall: an admissible set is conflict-free and defends all its arguments.

\begin{itemize}
    \item $\emptyset$ is trivially admissible.

    \item $\{d\}$ is admissible since $d$ has no attackers.

    \item $\{e\}$ is admissible since $e$ has no attackers.

    \item $\{d,e\}$ is admissible since neither $d$ nor $e$ is attacked.

    \item $\{b,d,e\}$:
    \begin{itemize}
        \item $b$ is attacked by $a$ and $c$
        \item $d$ attacks $a$
        \item $e$ attacks $c$
    \end{itemize}
    hence all attackers of $b$ are counterattacked.
    Therefore:
    \[
    \{b,d,e\}
    \]
    is admissible.
\end{itemize}

Thus:
\[
\textit{adm}(AF)=
\{
\emptyset,
\{d\},
\{e\},
\{d,e\},
\{b,d,e\}
\}
\]

\textbf{Step 3: Complete extensions}

Recall: a complete extension is an admissible set containing all arguments it defends.

\begin{itemize}
    \item $\emptyset$ is not complete:
    since $d$ and $e$ are unattacked, $\emptyset$ defends them vacuously,
    but does not contain them.

    \item $\{d\}$ is not complete:
    it also defends $e$ vacuously, but does not contain $e$.

    \item $\{e\}$ is not complete:
    symmetrically, it defends $d$ but does not contain it.

    \item $\{d,e\}$ is not complete:
    it defends $b$ because:
    \[
    d \to a \to b
    \]
    and
    \[
    e \to c \to b
    \]
    but $b \notin \{d,e\}$.

    \item $\{b,d,e\}$:
    \begin{itemize}
        \item admissible
        \item contains all arguments it defends
    \end{itemize}
    hence complete.
\end{itemize}

Therefore:
\[
\textit{comp}(AF)=
\{
\{b,d,e\}
\}
\]

\textbf{Grounded extension}

The grounded extension is the $\subseteq$-minimal complete extension.

Since there is only one complete extension:
\[
\boxed{
\textit{grounded}(AF)=\{b,d,e\}
}
\]

\textbf{Preferred extension}

Preferred extensions are the $\subseteq$-maximal complete extensions.

Again, since there is only one complete extension:
\[
\boxed{
\textit{pref}(AF)=\{b,d,e\}
}
\]

\textbf{Stable extension}

Recall: a stable extension must:
\begin{itemize}
    \item be conflict-free
    \item attack every argument outside the set
\end{itemize}

Consider:
\[
\{b,d,e\}
\]

Arguments outside the set:
\[
\{a,c\}
\]

We have:
\[
d \to a
\]
and
\[
e \to c
\]

Hence every outside argument is attacked.

Therefore:
\[
\boxed{
\textit{stable}(AF)=\{b,d,e\}
}
\]

\textbf{Final observation}

In this framework:
\[
\textit{grounded}(AF)
=
\textit{pref}(AF)
=
\textit{stable}(AF)
=
\{b,d,e\}
\]

while naive semantics additionally accepts:
\[
\{a,c\},\quad
\{a,e\},\quad
\{c,d\}
\]

showing that naive semantics may accept sets that are not admissible.

\end{document}